Priors

### 2024-05-16 illustrations/priors.Rmd
Update prior figures

q_pl <- ggplot() +
  geom_density(
    data = q_dat,
    mapping = aes(x = x, linetype = activity),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_text(
    data = prev_est,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), vjust = -2, hjust = 1
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    labels = scales::percent_format(suffix = "")
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Quanta generation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")

@@

lambda_pl <- ggplot() +
  geom_density(
    data = lambda_dat,
    mapping = aes(x = x),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est_vir,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est_vir,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_text(
    data = prev_est_vir,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), vjust = -2
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, .05)),
    labels = scales::percent_format(suffix = "")
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Bacterial inactivation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")

>>>>

q_pl <- ggplot() +
  geom_density(
    data = q_dat,
    mapping = aes(x = x, linetype = activity),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_label(
    data = prev_est,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), vjust = 0, hjust = 1.05,
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Quanta generation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")

@@

lambda_pl <- ggplot() +
  geom_density(
    data = lambda_dat,
    mapping = aes(x = x),
    adjust = 2
  ) +
  geom_segment(
    data = prev_est_vir,
    mapping = aes(x = x, xend = x, y = 0, yend = y, color = study),
    linetype = "dotted"
  ) +
  geom_point(
    data = prev_est_vir,
    mapping = aes(x = x, color = study, y = y),
    shape = 17, size = 2
  ) +
  geom_label(
    data = prev_est_vir,
    mapping = aes(x = x, label = lab, color = study, y = y),
    size = 8 / cm(1), nudge_y = .05
  ) +
  scale_x_log10(
    expand = expansion(mult = c(0, .025)),
    breaks = c(1e-4, 1e-5, 1e-3, 1e-2, 1e-1, 1e0, 1e1, 1e2, 1e3, 1e4, 1e5)
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, .05))
  ) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(
    x = "Bacterial inactivation rate (quanta/h)",
    y = "Density"
  ) +
  theme_custom() +
  theme(legend.position = "none")
